Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-04-13 ms.tex
added figures on crosshatch from flat field.

>>>>

\subsection{Subpixel Crosshatching}
The flat field of the ALONG detector, which is used for NIRCam grism series, has a pronounced crosshatch pattern visible in Figure \ref{fig:crossHatchA5}.
The patterns are located at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ counter-clockwise from the $+$X direction of the detector.
The angle between these lines is thus 44.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{crosshatch_zoom.pdf}
\includegraphics[width=.49\columnwidth]{crosshatch_2d_power.pdf}
\caption{
The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
}\label{fig:crossHatchA5}
\end{figure}
